The likelihood surface

### 2015-08-04 likelihood-surface.Rmd
.

```{r setup, include=FALSE}
required.input <- c("modelfile","longwin","shortwin","leftwin","tlen")
if (!all(sapply(required.input,exists))) {
    stop("Not all required input (", paste(required.input[!sapply(required.input,exists)],collapse=", "), ") has been given.")
}
names(required.input) <- required.input
opt <- lapply( required.input, get )
opt$boundary <- "none"
source("context-inference-fns.R",chdir=TRUE)
library(MASS)
library(numDeriv)
library(pander)
if (!file.exists(modelfile)) { stop("Can't find ", modelfile) }
model.config <- fill.default.config( read.config(modelfile) )
model.config$fixfn <- parse.fixfn( model.config$fixfn, model.config$fixfn.params )
if (!exists("gmfile")) {
    gmfile <- file.path(dirname(modelfile),gsub("%",opt$longwin,model.config$genmatrix,fixed=TRUE))
}
if (file.exists(gmfile)) {
    load(gmfile)
} else { 
    cat("Can't find generator matrix ", gmfile, " -- making a new one.\n")
    genmatrix <- do.call( makegenmatrix,
                    c( list(
                        patlen=opt$longwin, 
                        mutpats=model.config$mutpats, 
                        selpats=model.config$selpats, 
                        selfactors=model.config$selfactors, 
                        boundary=opt$boundary, 
                        bases=model.config$bases, 
                        fixfn=model.config$fixfn ),
                        model.config$fixfn.params
                    )
                )
}
genmatrix@x <- do.call( update, c( list(G=genmatrix, mutrates=model.config$mutrates, selcoef=model.config$selcoef), model.config$fixfn.params ) )
projmatrix <- collapsepatmatrix( ipatterns=rownames(genmatrix), leftwin=opt$leftwin, rightwin=opt$longwin-opt$shortwin-opt$leftwin, bases=genmatrix@bases )
```

```{r expected_counts, include=FALSE}
total.counts <- 1e8
expected.counts <- predictcounts(opt$longwin, opt$shortwin, opt$leftwin, initcounts=rep(total.counts/nrow(genmatrix),nrow(genmatrix)), genmatrix=genmatrix, projmatrix=projmatrix, tlen=opt$tlen)

@@

And, the pairwise profiles of the likelihood:
```{r pairwise_prof, echo=FALSE}
likfun.grids <- likelihood.surface( model, tlen=opt$tlen )
```

>>>>

```{r setup, include=FALSE}
required.input <- c("modelfile","longwin","shortwin","leftwin","tlen","ncounts")
if (!all(sapply(required.input,exists))) {
    stop("Not all required input (", paste(required.input[!sapply(required.input,exists)],collapse=", "), ") has been given.")
}
names(required.input) <- required.input
opt <- lapply( required.input, get )
opt$boundary <- "none"
if (!exists("lik.grid")) { lik.grid <- 10 }
source("context-inference-fns.R",chdir=TRUE)
library(MASS)
library(numDeriv)
library(pander)
if (!file.exists(modelfile)) { stop("Can't find ", modelfile) }
model.config <- fill.default.config( read.config(modelfile) )
model.config$fixfn <- parse.fixfn( model.config$fixfn, model.config$fixfn.params )
if (!exists("gmfile")) {
    gmfile <- file.path(dirname(modelfile),gsub("%",opt$longwin,model.config$genmatrix,fixed=TRUE))
}
if (file.exists(gmfile)) {
    load(gmfile)
} else { 
    cat("Can't find generator matrix ", gmfile, " -- making a new one.\n")
    genmatrix <- do.call( makegenmatrix,
                    c( list(
                        patlen=opt$longwin, 
                        mutpats=model.config$mutpats, 
                        selpats=model.config$selpats, 
                        selfactors=model.config$selfactors, 
                        boundary=opt$boundary, 
                        bases=model.config$bases, 
                        fixfn=model.config$fixfn ),
                        model.config$fixfn.params
                    )
                )
}
genmatrix@x <- do.call( update, c( list(G=genmatrix, mutrates=model.config$mutrates, selcoef=model.config$selcoef), model.config$fixfn.params ) )
projmatrix <- collapsepatmatrix( ipatterns=rownames(genmatrix), leftwin=opt$leftwin, rightwin=opt$longwin-opt$shortwin-opt$leftwin, bases=genmatrix@bases )
```

Here is an estimate of the likelihood surface near the true values for the model in `r modelfile`,
at tuple size:

*  *longwin* : `r opt$longwin`
*  *shortwin* : `r opt$shortwin`
*  *leftwin* : `r opt$leftwin`
and other parameters
*  *total time* : `r opt$tlen`  (`tlen`)
*  *number of counts* : `r opt$ncounts`  (`ncounts`)
*  *number of grid points for likelihood* : `r lik.grid` (`lik.grid`)

```{r expected_counts, include=FALSE}
expected.counts <- predictcounts(opt$longwin, opt$shortwin, opt$leftwin, initcounts=rep(ncounts/nrow(genmatrix),nrow(genmatrix)), genmatrix=genmatrix, projmatrix=projmatrix, tlen=opt$tlen)

@@

And, the pairwise profiles of the likelihood:
```{r pairwise_prof, echo=FALSE}
likfun.grids <- likelihood.surface( model, tlen=opt$tlen, ngrid=lik.grid )
```
